\documentclass[margin]{res}
\newsectionwidth{0.9in}
%\setlength{\resumewidth}{160mm}
%\setlength{\sectionwidth}{50mm}
%\setlength{\rightmargin}{20mm}
\usepackage{color}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{url}
\usepackage{setspace}
\pagestyle{fancy}
%\newlength{\margintotal}% Save total margin width
%\setlength{\margintotal}{\marginparsep+\marginparwidth}
%\fancyheadoffset[LE,RO]{-0.1in}
\fancyheadoffset[LO]{0.9in}
\fancyheadoffset[RE]{-0.5in}
\topmargin = -0.5in
%\belowmargin = -0.6in
%\buttommargin = -0.6in
\addtolength{\oddsidemargin}{-0.4in}
\addtolength{\textwidth}{0.8in}
\addtolength{\textheight}{1.5in}
\lhead{\small{$\bullet$ E-mail: {chenyu.huang@outlook.com} \\$\bullet$ Phone: +1 (858) 281 1385}}
\rhead{\small{$\bullet$ Address: One Miramar Street \#929764,\\ La Jolla, CA, 92092}}
\chead{\Large{\bf{Chenyu HUANG}}}

%\lfoot{}
%\rfoot{}
\renewcommand{\headrulewidth}{0pt}
%\cfoot{}
\renewcommand{\rmdefault}{ppl}
\linespread{0.94}
\DeclareFixedFont{\titlefont}{OT1}{qbk}{m}{n}{16pt}
%\usepackage{helvetica}
\begin{document}
    \begin{resume}
    	\vskip 3ex
		%\centerline{\small\hfill{ $\bullet$ +86-18818212465 }}
		%\begin{spacing}{0.5}\end{spacing}
   		%\hspace{2mm}{\titlefont Curriculum Vitae}}}
	    % Draw a horizontal line the whole width of resume:
	    \moveleft\hoffset\vbox{\hrule width 7.3in height 1.2pt}\smallskip
		\begin{spacing}{0.8}\end{spacing}
    	% address begins here
    	% Again, the address lines must be centered over entire width of resume:
    	% \moveleft0.68 \hoffset\centerline{\bf \large OBJECTIVE: A full-time technical position as an software developer or project manager.}
    	% \begin{spacing}{2.0}\end{spacing}
    	\vskip -3ex
    	\vskip -3ex
    	
    		\section{\large{O}\normalsize{bjective}}
    		Expected to graduate in December 2017, seeking for a \textbf{full time software development} role.    		\vskip -2.5ex
        \vskip -3ex 
    	
        \section{\large{E}\normalsize{ducation}}
        \textbf{University of California, San Diego (UCSD)}, San Diego, CA \hfill \emph{Sep. 2016 - Dec. 2017 (Expected)} \\
            Master of Science in Computer Science, GPA: \textbf{\textit{3.72/4.0}}\\
            \vskip -4ex
        
        \textbf {Nanyang Technological University (NTU)}, Singapore  \hfill \emph{Aug. 2012 - Jun. 2016} \\
            Bachelor of Engineering in Electrical \& Electronic Engineering, GPA: \textbf{\textit{4.62/5.0, 1st class honors}}\\
            \vskip -4ex
            \vskip -3ex

        \section{\large{W}\normalsize{ork} \large{E}\normalsize{xperience}}
        \textbf {Software Engineering Intern}, \textbf{Mitek System, Inc}, \emph{San Diego, CA} \hfill \emph{Jun. 2017 - Sep. 2017}
        	\begin{itemize} \itemsep -2pt
		\item Worked in an \textbf{\textit{Agile}} and \textbf{\textit{Test Driven}} environment developing \textbf{\textit{Android}} SDKs in \textbf{\textit{Java}}
		\item Developed and shipped MobileDocs SDK for high resolution document capture for \textbf{\textit{Android}} devices
		\item Optimized existing MiSnap SDK reducing the SDK size by \textbf{\textit{over 30\%}} via dynamic asset generation
		\item Automated \textbf{\textit{unit tests}} using \textbf{\textit{JUnit}} and \textbf{\textit{Roboelectric}}, continuous build and integration with \textbf{\textit{Jenkins}}
        	\end{itemize}
	\vskip -1.5ex
	\textbf {Research Assistant}, \textbf{SeeLab UCSD}, \emph{San Diego, CA} \hfill \emph{Jun. 2017 - Present}
		\begin{itemize} \itemsep -2pt
        		\item Worked with PhD candidates developing high performance, low power \textbf{\textit{classifiers}}
		\item Implemented high performance \textbf{\textit{Hierarchical Hyper Vector}} based voice \textbf{\textit{classifier}}
		\item Achieved the same accuracy as conventional \textbf{\textit{Neural Network}}, but with \textbf{\textit{over 50\%}} saving in energy
        	\end{itemize}
	\vskip -1.5ex
        	\textbf {Software Engineering Intern}, \textbf{Rolls-Royce Corporation}, \emph{Singapore} \hfill \emph{Jan. 2015 - May. 2015}
        	\begin{itemize} \itemsep -2pt
        		\item Developed data driven web applications using \textbf{\textit{D3.js}} to visualize engine service data 
		\item Scripted in \textbf{\textit{Python}} to predict engine failure types using \textbf{\textit{Bags of words}} model
		\item Responsive web development using \textbf{\textit{Bootstrap, jQuery, media query etc}}
        	\end{itemize}
        	\vskip -2ex
        	\vskip -3ex
        	
        \section{\large{A}\normalsize{cademic} Projects}
        			\textbf{Column-based Scalable Database} \hfill \emph{May - Jun 2017}
        	\begin{itemize} \itemsep -2pt
        			\item Designed and implemented an \textbf{\textit{NoSQL column-based}} database system in \textbf{\textit{Java}}
			\item Implemented the database with \textbf{\textit{Memtable}} to store recent data and \textbf{\textit{SSTable}} to store \textbf{\textit{long-tail}} data
			\item Implemented a \textbf{\textit{Bloom Filter}} to efficiently determine membership status of any data entry
			\end{itemize}
			\vskip -2ex
					
			\textbf{Custom Branch Predictor} \hfill \emph{May. 2017}
        	\begin{itemize} \itemsep -2pt
        			\item Implemented the \textbf{\textit{gshare}} and \textbf{\textit{tournment}} branch predictors in \textbf{\textit{C++}}
			\item Designed a custom predictor in \textbf{\textit{C++}} by combining \textbf{\textit{gshare}} and a \textbf{\textit{2-level local}} predictor
			\item Custom predictor achieves \textbf{97\%} of accuracy on given test data, a \textbf{7\%} improvements over \emph{gshare} 
			\end{itemize}
			\vskip -2ex
        
        			\textbf{Web Mining and Recommender Systems} \hfill \emph{Jan. 2017 - Mar. 2017}
        		\begin{itemize} \itemsep -2pt
        		\item Applied the techniques of  \textbf{\textit{Regression, Classification}} to build a rating predictor system in  \textbf{\textit{Python}}
		\item Implemented a  \textbf{\textit{Latent Factor Model}} in  \textbf{\textit{Python}} to predict user ratings of their Amazon purchases
		\item Trained the system using 200,000 entries of anonymous review data from Amazon
		\item Achieved an mean square error of 12.6 for rating prediction on a scale of 100
			\end{itemize}
			\vskip -2ex
			
			\textbf{Computer Vision} \hfill \emph{Sep. 2016 - Dec. 2016}
        	\begin{itemize} \itemsep -2pt
         		\item Implemented image formation of \textbf{\textit{perspective camera model}} with different camera parameters.
 			\item Implemented a face recognition algorithm based on \textbf{\textit{Eigenfaces and Principle Component Analysis.}}
 			\item Implemented the \textbf{\textit{Lucas-Kanade algorithm}} to estimate optical flow between image frames.
 			\end{itemize}
 			\vskip -2ex
			
		\textbf{Probabilistic Learning} \hfill \emph{Sep. 2016 - Nov. 2016}
        	\begin{itemize} \itemsep -2pt
        		\item Implemented a set of learning algorithms in \textbf{\textit{Java}} and \textbf{\textit{Matlab}}, including \textbf{\textit{maximum likelihood, EM}}
				\item Implemented multiple \textbf{\textit{Markov language models}}, e.g  \textbf{\textit{unigram, bigram and mixture models}} in \textbf{\textit{Java}} 
				\item Implemented a \textbf{\textit{Markov decision model}} for a puzzle solving agent using \textbf{\textit{value and policy iteration}}
			\end{itemize}
			\vskip -2ex	
			
			\textbf{Online Movie Ticket Reservation System} \hfill \emph{Aug. 2015 - Nov. 2015}
         	\begin{itemize} \itemsep -2pt
         		\item Developed a movie ticket booking system supporting seat-picking, synopsis and user rating.
 			\item Implemented the backend with \textbf{\textit{MySql}} and \textbf{\textit{PHP}} to update and retrieve information from database
 			\item Designed and implemented a \textbf{\textit{responsive}} user interface using \textbf{\textit{HTML, CSS}} and \textbf{\textit{JavaScript}}
 			\end{itemize}
			
			\vskip -2ex
			\vskip -4ex

	\section{\large{P}\normalsize{ersonal} Projects}
	\textbf{Android Development} \hfill \emph{Jul. 2017}\\
			{\sl Dark World Game for Android}
        	\begin{itemize} \itemsep -2pt
		\item Developed a puzzle game based on the  \textbf{\textit{Model-View-Presenter}} development paradigm
		\item Dynamically generates puzzle maps based on player's configuration
		\item Implemented fully  \textbf{\textit{gesture based}} with  \textbf{\textit{buttonless}} game controls
		\end{itemize}
		\vskip -2ex
	
			{\sl GRE Vocabulary Builder for Android}
        	\begin{itemize} \itemsep -2pt
        		\item Developed an Android app to help students prepare for GRE verbal tests
		\item Connected to Android's  \textbf{\textit{text-to-speech API}} to provide pronunciations for all words
		\item Designed a \textbf{\textit{relational SQLite}} database to store user performance data and support predictive search
		\item Connects to  \textbf{\textit{Restful API}} to provide word definition for words not in local database
			\end{itemize}
			\vskip -2ex
	
		{\sl Robotics Controller for Android}
		\begin{itemize} \itemsep -2pt
		\item Developed an \textbf{Android} app to remotely control a robot via  \textbf{\textit{Bluetooth}}
		\item Utilized internet protocol to wirelessly stream live video (30fps) from the robot's camera
		\end{itemize}

		\vskip -1.5ex
		\vskip -3ex

        \section{\large{C}\normalsize{omputer} \large{S}\normalsize{kills}}
			\textbf{\emph{Java, Python, Matlab, C++, SQL, HTML, JavaScript, CSS, PHP, Latex}}\\
    \end{resume}
\end{document}
