%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Chenyu}{ Huang}
\address{One Miramar Street, 929764, La Jolla, CA 92092, United States of America}
\mobile{ (+1)-858-281-1385} 
%%% Social
\email{chh217@eng.ucsd.edu}
%%\github{posquit0}
%%\linkedin{posquit0}
%%% Optionals
%%\position{Software Engineer{\enskip\cdotp\enskip}Security Expert}
\position{Masters Degree student in Computer Science{\enskip\cdotp\enskip}University of California San Diego}
\quote{``Life, from the moment of birth to death, is a process of learning."}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
  {Company Recruitment Team}
  {AppLovin}
\letterdate{\today}
\lettertitle{Job Application for Software Engineer Intern}
\letteropening{Dear Recruiter,}
\letterclosing{Sincerely,}
%%\letterenclosure[Attached]{Curriculum Vitae}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Chenyu Huang~~~·~~~Cover Letter}
  {}

\begin{document}
%%% Make a header for CV using personal data
\makecvheader

%%% Make a title for Cover Letter using letter data
\makelettertitle

%%% Write content for your cover letter
\begin{cvletter}
\cvparagraph{About Me}
My name is Chenyu. I am currently a Masters student in computer science at UCSD. As a student at UC San Diego, my coursework in machine learning afforded me the opportunity to learn additional programming languages such as Python. My recent endeavor includes building a rating prediction system in Python using techniques of regression, classification and clustering. At the same time, I am doing a personal project developing an Android application (Java) to help student prepare for GRE verbal test. It incorporates a streamlined UI, a SQLite database to store vocabulary and user data, while also connects to third party API to provide definition for words not in the database. 

Prior to my arrival to UC San Diego, I pursued my undergraduate degree at Nanyang Technological University in Singapore. Among the numerous projects I conducted as an undergraduate, I developed an online movie ticket reservation website with HTML, JavaScript, CSS and MySQL, and as part of my final year project for my undergraduate study, I developed Java application to simulate the ground vehicle operations at Singapore’s Changi Airport.

In addition to project experience in school, I have stepped into the industry as a software engineer intern at Rolls-Royce for the first half of 2015. There, I was in charge of developing data visualization web application using D3.js. Besides that, I also spent a fair amount of time developing responsive web applications using Bootstrap and Media query.

\cvparagraph{Why do I want to work in Palo Alto}
The Bay Area is where my life in America started. When I first visited the Bay Area in 2013 as an undergraduate exchange student at UC Berkeley, I was amazed by the width and depth of its technology industry. This strongly influenced my decision of furthering my career in technology by continuing a masters degree in Computer Science. I want to work in Palo Alto for its great weather and scenery, and more importantly to remind myself why I love what I do.   

\cvparagraph{Summary}
Being incredibly passionate about software, I am eager to step into industry and get hands-on experience. I want to further strengthen my skills in web and mobile development and advance my career as a full stack and mobile developer. I hope you would consider me for this position, and I look forward to discussing it further with you. 
\end{cvletter}

%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}
